Joint training of classification model and similarity model for low-resource text classification in chatbot

### 2020-08-26 chatbot_classification/aaai_2021/paper.tex
modified:   paper.pdf   modified:   paper.tex

  \begin{abstract}
    Building  conversational  chatbot  system  has  become a popular solution to
    customer services under various business scenarios. A conversational chatbot
    needs to detect user's intent given a few words, which essentially equals to
    short-text   classification   problem  in  the  field  of  Natural  Language
    Processing. Moreover, each time for a new service, the task-specific chatbot
    system  often  needs  to  perform  well  in  few-shot  setups due to lack of
    domain-specific  data,  which  is  quite a challenge for single-model system
    such   as   text  classification  model  system  or  sentence-pair  semantic
    similarity  model  system under such a low-resource condition. Therefore, in
    this  paper, we propose SFC, a 2-stage joint system with multi-task training
    technique  for  both  text  classification  task  and sentence-pair semantic
    similarity  task  to  overcome  this challenge. Furthermore, we additionally
    propose  an  improved  version of SFC to allow text classification model and
    sentence-pair model be combined into a joint model organized in hierarchical
    structure.  We  also conduct extensive experiments on 4 public and 1 private
    datasets  in  few-shot  setup  (i.e.,  with  only  5 to 20 training data per
    class).   The  experimental  results  show  that  our  system  can  steadily
    outperform  several  competitive  single-model  baselines  by  2  percent in
    average accuracy.
  \end{abstract}

  \section{Introduction}
  \label{sec:intro}
  Task-specific  conversational  chatbot\cite{wen2016network}  are  designed  to
  share   the  working  pressure  of  human  customer  service  agents  who  are
  responsible for solving customers' questions or queries about certain products
  or  services.  Regardless  of  whether  the  conversation  is  single-turn  or
  multi-turn,  the  essential  technical  solution  behind the chatbot is intent
  classification model which can identify the correct intent behind user's input
  text and find the corresponding answer.

  Although  task-specific  conversational chatbot already has a wide application
  in various business and industries, it's still a quite challenging task due to
  its  natural  properties of low-resource. First, customers' utterance within a
  conversation  is  usually  quite  short  and  completed  in a few words. Short
  text\cite{song2014short}  are generally more ambiguous in comparison with long
  texts  such  as  paragraphs  or  documents  since  they  don't  contain enough
  contextual  information,  which poses a great challenge\cite{chen2019deep} for
  classification        task\cite{phan2008learning,yan2009dynamic,hua2015short}.
  Second,  at  the  initial  stage  of  building  a chatbot for specific task or
  service, it's often extremely hard to collect sufficient data samples for each
  class.  The  reason  is  that it's usually too expensive and time consuming to
  extract  different  ways  of natural language expression for each intent class
  from  history  conversation  log  or  even  manually  compose  the corpus from
  nothing.  Therefore,  the  key  to  building a task-specific chatbot with high
  performance     becomes     solving     the     challenge     of    short-text
  classification\cite{sriram2010short}        problem       under       few-shot
  setting\cite{yu2018diverse}.

@@

  One  of  the most popular approach among existing work was text classification
  model  based  on  neural network. Since the length of the text is quite short,
  many   previous   work\cite{wen2016network}  choose  neural  network  such  as
  convolutional                          neural                         networks
  (CNNs)\cite{kim2014convolutional,zhang2015character,conneau2016very}  or  long
  short  term memory networks (LSTMs)\cite{mousa2017contextual,liu2016recurrent}
  to  accomplish  the task of extracting semantic feature from limited amount of
  words.  A  common model structure is adding a softmax classifier to the top of
  the  neural  network.  Afterwards, pre-trained language models on large corpus
  like   BERT\cite{devlin2018bert}  and  RoBERTa\cite{liu2019roberta}  has  been
  proven   more   powerful  in  solving  many  NLP  tasks  including  short-text
  classification\cite{madabushi2020cost}.      Especially      for      few-shot
  scenarios\cite{yu2018diverse},       pre-trained      model      based      on
  transformers\cite{vaswani2017attention},   shown  in  Fig.  \ref{Fig.1.sub.1},
  tends  to do more help to reducing the negative effects brought by scarcity of
  training data.

  Another  common  approach  is  text  classification  neural  network  based on
  label-word     joint     embedding,    such    as    LEAM\cite{wang2018joint},
  MTLE\cite{zhang2017multi}   and   EXAM\cite{du2019explicit}.   This   approach
  involves  label  embedding when constructing the text-sequence representation.
  Take  LEAM  as  an  example,  the  text classification model is implemented by
  jointly    embedding    the    word    and    label   in   the   same   latent
  space\cite{wang2018joint}. Afterwards, the text representation are constructed
  based  on  text-label  compatibility through attention mechanism. In this way,
  additional  sources  of  semantic  information  from class labels can be fully
  leveraged, which is quite helpful especially under few-shot scenario.

  The  third  popular  approach  among  previous work was based on sentence-pair
  model.  The  motivation  of  this  approach  was  started  from  the  idea  of
  Information     Retrival    (IR)    based    chatbot\cite{jafarpour2010filter,
  leuski2011npceditor}.  Having  a  Q-A (Question-Answer) pairs dataset and user
  query  Q,  the  IR based conversational system will look up in the Q-A dataset
  for  the pair (Q', A') that best matches query Q through semantic analysis and
  returns   A'   as   the  answer  to  Q\cite{mnasri2019recent}.  In  this  way,
  sentence-pair  model  pre-trained  on  large  corpus  of  semantic  similarity
  identification  task  can  be applied for being used as a tool to identify the
  class  with  highest  semantic  similarity to customer's query. A common model
  structure  of pre-trained\cite{devlin2018bert} sentence-pair model is based on
  multiple  cross-attention  mechanism\cite{barkan2020scalable},  shown  in Fig.
  \ref{Fig.1.sub.2}.  Due  to  the  fact that many experiment results have shown
  that  RoBERTa\cite{liu2019roberta}  is  an  improved  version of BERT, and has
  achieved  amazing  results  on  both  text  classification  and sentence-pairs
  semantic similarity tasks, we choose RoBERTa as an important baseline approach
  in this paper.

  Despite the success of these 3 approaches, they still have some limitations in
  task-specific chatbot scenario. As for the text classification model approach,
  it's   quite   hard  to  use  data  augmentation  method  to  solve  the  data
  insufficiency  challenge since the it's usually unfeasible to get large amount
  of  domain-specific  data  when  facing  a  new  task. As for label-word joint
  embedding  approach,  it  poses  noticeable requirements on label information.
  However,  in  our  cases,  since  we have large amount of class labels without
  being well-defined for question answering chatbot, the only thing we can do is
  to  choose  one  of the user utterance as the class label to represent the key
  information  of  the  whole class. In this way, the label will become not only
  prolix  but  also  biased,  which  will  bring  some  negative effect to label
  embedding.  With  respect  to  the sentence-pair model approach, though we can
  obtain   large   amount  of  data  in  semantically  duplicate  sentence  pair
  identification  domain  for  transfer  learning\cite{sun2019fine},  it's still
  quite  hard  to  perform  well  on  task-specific dataset because the training
  objective  of  sentence-pair  model  is semantic similarity, which is slightly
  different from the target of classification task. That is to say, there always
  exists  some intent classes which cannot be distinguished by each other merely
  depending on semantic similarity. For example, we have 2 user query saying, A:
  What  should I do if I want to change my password? B: What is the modification
  rule if I want to change my password? In this case, sentence A is semantically
  similar  to  B,  since  they  both  express  the desire for changing password.
  However, it's still reasonable to classify them into 2 intent classes, since A
  is asking for the method for changing password, while B is asking for the rule
  to follow when creating a new password.

@@

  The  above  limitation  motivates  us  to  propose a joint system of both text
  classification  task  and  sentence-pair  semantic  similarity task, named SFC
  here, shown in Fig. \ref{fig:ver.1.3}. Our goal is to utilize the advantage of
  the  feasibility  of  transfer learning based on semantic similarity, while in
  the  mean time, add the classification task's target into the training process
  of            sentence-pair           model           for           multi-task
  learning\cite{caruana1993multitask,collobert2008unified}.  To  obtain  such  a
  joint  system,  we  first start with preparation work, which is pre-training a
  sentence-pair   model   on  external  corpus  for  sentence  pair  duplication
  identification,  and  then  find  an auxiliary model or tool which can help us
  sample out top-K most related intent classes. This auxiliary model or tool can
  either  be searching engine such as elasticsearch\cite{divya2013elasticsearch}
  or  a  text  classification  model  trained  on  task-specific  chatbot  data.
  Afterwards,  we  further  fine-tune  the  sentence-pair  model with 2 training
  tasks:  1)  the  regular  sentence pair similarity tasks. Here we use the text
  classification  model  as  an auxiliary model in this paper to sample sentence
  pairs       for       training       based      on      negative      sampling
  strategy\cite{bamler2020extreme}.  The  reason is that a task-specific chatbot
  often  has hundreds of intent classes, which forms too many sentence pairs for
  training  since  any  two  sentences  from  two  different  classes can form a
  sentence-pair     of     negative     sample.     Besides,     according    to
  Bamler\cite{bamler2020extreme},   training   on  negative  samples  from  most
  confusing  wrong  label  can  help  model  converge  faster  and obtain better
  performance.  2) the classification task on top-K (here K is a hyperparameter)
  candidate  classes  provided  by  our auxiliary model or tool. Here we use the
  average  pooling  of  the  representation  given  by  sentence-pair  model for
  sentence pairs formed by the user input query and the corpus sentences in each
  class  as  the  feature.  We  stack the task-specific layers on the top of the
  shared-parameter  sentence-pair  model structure, which is a classic parameter
  sharing                                   mechanism\cite{collobert2008unified,
  subramanian2018learning,liu2019multi}   for  multi-task\cite{sun2019fine}.  In
  this  way, specific knowledge contained in these 2 tasks can be fully explored
  and deeply interact with each other to obtain better overall performance.

  However,  since  the auxiliary tool in joint system mentioned above works in a
  separate  stage  from  sentence-pair model, we find the the quality of sampled
  candidate  classes  might  limit  the  overall  performance  of SFC, since the
  candidate  classes  for  each user query is always fixed during the multi-task
  training  process. This observation motivates us to further improve SFC into a
  joint  model  of  sentence-pair  model  and  text  classification  model  in a
  hierarchical  architecture  by  putting  different  tasks at different network
  layers\cite{sogaard2016deep,   hashimoto2016joint}   and  then  training  them
  together,  shown  in  Fig  \ref{fig:framework}.  Here, the text classification
  model  involved in joint training process replace the role of auxiliary tools.
  In  this  way, the sentence pairs selected from top-K classes becomes dynamic,
  which  means  the  text classification model will also be further optimized to
  provide better top-K classes pooling result.

@@

  Before we start to fine-tune our sentence-pair model on task-specific dataset,
  we   first  fine-tune  RoBERTa  on  Quora  dataset\cite{iyer2017first},  which
  contains  404,290  potential  duplicate question pairs, for transfer learning.
  Then   we   continue  to  do  multi-task  training  on  sentence-pair  dataset
  $\mathcal{D'}$ sampled from the top-K candidate class labels provided by stage
  1.

@@

  \textbf{Amazon-670K}   is   a   customer   product  review  dataset  for  text
  classification  task from the extreme classification repository with full data
  containing  670,091  class  labels,  285,176  training samples and 150875 test
  samples\cite{bhatia2016extreme}.  As  the  data  set  contains  multiple class
  labels  per  training sample, we keep only the first class label for each data
  point. Besides, we also randomly sampled 250 class labels from all the classes
  that  contain only 5-15 data points. In this way, we simulate the low-resource
  chatbot  corpus setting with the subset of 1,942 training samples and 716 test
  samples for 250 class labels.

@@

  \textbf{HWU64}   is  a  intent  detection  dataset  designed  for  home  robot
  scenario\cite{liu2019benchmarking}.  It aims at the specific task of capturing
  the  intent  for  different  user  requests  to  home  robot  and  finding the
  corresponding answer. The raw dataset contains 25,716 data points for 64 class
  labels  through  crowdsourcing,  which  raises  much  more  data  than  common
  real-world  circumstances. Therefore, we experiment with the setups where only
  5,  10,  15  and 20 training data points are available for each class label by
  random sampling.

  \textbf{CLINC150}  is a dataset designed for task-oriented systems with 23,700
  queries  that  are  short  and unstructured for 150 intents, in the same style
  made  by real users through crowdsourcing\cite{larson2019evaluation}. Here, we
  sample 5, 10 and 15 training data points for each intent class label by random
  sampling for our experimental setup.

  \textbf{BANKING77}  is  a intent detection dataset for bank customer services.
  The    raw    dataset    contains    13,084   data   points   for   77   class
  labels\cite{casanueva2020efficient}.  Here,  we  sample 5, 10, 15, 20 training
  data  points  for  each  class  label  by random sampling for our experimental
  setup.

@@

  \textbf{Group  1:  single-task  classification  model.} This group of baseline
  models  are  based  on the network structure for classification model shown in
  \ref{Fig.1.sub.1}.   As   for   non-pretrained   neural   network,  we  choose
  TextCNN\cite{kim2014convolutional}  as  a  representative baseline. As for the
  pretrained  model,  we choose RoBERTa, BERT and ALBERT, all of which are among
  the  most  powerful pretrained models that achieve outstanding results in many
  NLP  tasks,  in  our  experimental  setting. Since we apply RoBERTa in our SFC
  system,   we   naturally  adopt  single-task  classification  model  based  on
  RoBERTa-large  and RoBERTa-base as our baseline models. Besides, we also adopt
  the       recently       released       baseline       pre-trained       model
  ALBERT-xxlarge\cite{lan2019albert}  for  comparison.  Since  we  use different
  few-shot   settings   from   \cite{casanueva2020efficient}  for  those  intent
  detection  datasets,  we also use BERT-large tuned on our few-shot settings as
  an essential reference for experimental results.

>>>>

  \begin{abstract}
    Task-specific  chatbot  systems has gained many important applications, such
    as  Siri, Google home, customer service systems to allievaite human's labor.
    In  this  kind  of  systems, one of the core problems is the accurate detection of
    intention  of  a  user's input. It is then mapped into a predefined chatting
    logic  graph,  and the chatbot can return reasonable answers easily. This is
    the  main  difference from a free chatbot. The intention detection, assuming
    only  one  intention  in  a  sentence,  can  be  modeled  as  a  short  text
    classification  problem.  In  practice,  the  number  of  intentions  can be
    hundreads of thousands, as opposed to quite limited in the tradiational text
    classification  problem,  and  the  labeled  data  is not trivial to acquire
    plenty,  generally  10  to 20 per intention. Then, how to train an efficient
    model  in such a resource-intensive practical application in a new domain is
    critical.  In  this  work, we propose a novel model, called similairty model
    fused with classification Model (SFC), which combines a classification model
    and  a  similairty  model,  and  borrows the power of multi-task training as
    well.  We  conduct extensive experiments on 4 public and 1 private datasets.
    The  experimental  results  show  that our new model outperforms very strong
    baselines, BERT, RoBERTa and ALBERT based pretrained models by 2 percentages
    in average accuracy.

  \end{abstract}

  \section{Introduction}
  \label{sec:intro}

  todo: joint training of intention and NER.

  Task-specific  conversational  chatbot  \cite{wen2016network}  are  designed  to
  share   the  working  pressure  of  human  customer  service  agents  who  are
  responsible for solving customers' questions or queries about certain products
  or  services.  Regardless  of  whether  the  conversation  is  single-turn  or
  multi-turn,  the  essential  technical  solution  behind the chatbot is intent
  classification model which can identify the correct intent behind user's input
  text and find the corresponding answer.

  Although  task-specific  conversational chatbot already has a wide application
  in various business and industries, it's still a quite challenging task due to
  its  natural  properties of low-resource. First, customers' utterance within a
  conversation  is  usually  quite  short  and  completed  in a few words. Short
  text \cite{song2014short}  are generally more ambiguous in comparison with long
  texts  such  as  paragraphs  or  documents  since  they  don't  contain enough
  contextual  information,  which poses a great challenge \cite{chen2019deep} for
  classification        task \cite{phan2008learning,yan2009dynamic,hua2015short}.
  Second,  at  the  initial  stage  of  building  a chatbot for specific task or
  service, it's often extremely hard to collect sufficient data samples for each
  class.  The  reason  is  that it's usually too expensive and time consuming to
  extract  different  ways  of natural language expression for each intent class
  from  history  conversation  log  or  even  manually  compose  the corpus from
  nothing.  Therefore,  the  key  to  building a task-specific chatbot with high
  performance     becomes     solving     the     challenge     of    short-text
  classification \cite{sriram2010short}        problem       under       few-shot
  setting \cite{yu2018diverse}.

@@

  One  of  the most popular approach among existing work was text classification
  model  based  on  neural network. Since the length of the text is quite short,
  many   previous   work \cite{wen2016network}  choose  neural  network  such  as
  convolutional                          neural                         networks
  (CNNs) \cite{kim2014convolutional,zhang2015character,conneau2016very}  or  long
  short  term memory networks (LSTMs) \cite{mousa2017contextual,liu2016recurrent}
  to  accomplish  the task of extracting semantic feature from limited amount of
  words.  A  common model structure is adding a softmax classifier to the top of
  the  neural  network.  Afterwards, pre-trained language models on large corpus
  like   BERT \cite{devlin2018bert}  and  RoBERTa \cite{liu2019roberta}  has  been
  proven   more   powerful  in  solving  many  NLP  tasks  including  short-text
  classification \cite{madabushi2020cost}.      Especially      for      few-shot
  scenarios \cite{yu2018diverse},       pre-trained      model      based      on
  transformers \cite{vaswani2017attention},   shown  in  Fig.  \ref{Fig.1.sub.1},
  tends  to do more help to reducing the negative effects brought by scarcity of
  training data.

  Another  common  approach  is  text  classification  neural  network  based on
  label-word     joint     embedding,    such    as    LEAM \cite{wang2018joint},
  MTLE \cite{zhang2017multi}   and   EXAM \cite{du2019explicit}.   This   approach
  involves  label  embedding when constructing the text-sequence representation.
  Take  LEAM  as  an  example,  the  text classification model is implemented by
  jointly    embedding    the    word    and    label   in   the   same   latent
  space \cite{wang2018joint}. Afterwards, the text representation are constructed
  based  on  text-label  compatibility through attention mechanism. In this way,
  additional  sources  of  semantic  information  from class labels can be fully
  leveraged, which is quite helpful especially under few-shot scenario.

  The  third  popular  approach  among  previous work was based on sentence-pair
  model.  The  motivation  of  this  approach  was  started  from  the  idea  of
  Information     Retrival    (IR)    based    chatbot \cite{jafarpour2010filter,
  leuski2011npceditor}.  Having  a  Q-A (Question-Answer) pairs dataset and user
  query  Q,  the  IR based conversational system will look up in the Q-A dataset
  for  the pair (Q', A') that best matches query Q through semantic analysis and
  returns   A'   as   the  answer  to  Q \cite{mnasri2019recent}.  In  this  way,
  sentence-pair  model  pre-trained  on  large  corpus  of  semantic  similarity
  identification  task  can  be applied for being used as a tool to identify the
  class  with  highest  semantic  similarity to customer's query. A common model
  structure  of pre-trained \cite{devlin2018bert} sentence-pair model is based on
  multiple  cross-attention  mechanism \cite{barkan2020scalable},  shown  in Fig.
  \ref{Fig.1.sub.2}.  Due  to  the  fact that many experiment results have shown
  that  RoBERTa \cite{liu2019roberta}  is  an  improved  version of BERT, and has
  achieved  amazing  results  on  both  text  classification  and sentence-pairs
  semantic similarity tasks, we choose RoBERTa as an important baseline approach
  in this paper.

  Despite the success of these 3 approaches, they still have some limitations in
  task-specific chatbot scenario. As for the text classification model approach,
  it's   quite   hard  to  use  data  augmentation  method  to  solve  the  data
  insufficiency  challenge since the it's usually unfeasible to get large amount
  of  domain-specific  data  when  facing  a  new  task. As for label-word joint
  embedding  approach,  it  poses  noticeable requirements on label information.
  However,  in  our  cases,  since  we have large amount of class labels without
  being well-defined for question answering chatbot, the only thing we can do is
  to  choose  one  of the user utterance as the class label to represent the key
  information  of  the  whole class. In this way, the label will become not only
  prolix  but  also  biased,  which  will  bring  some  negative effect to label
  embedding.  With  respect  to  the sentence-pair model approach, though we can
  obtain   large   amount  of  data  in  semantically  duplicate  sentence  pair
  identification  domain  for  transfer  learning \cite{sun2019fine},  it's still
  quite  hard  to  perform  well  on  task-specific dataset because the training
  objective  of  sentence-pair  model  is semantic similarity, which is slightly
  different from the target of classification task. That is to say, there always
  exists  some intent classes which cannot be distinguished by each other merely
  depending on semantic similarity. For example, we have 2 user query saying, A:
  What  should I do if I want to change my password? B: What is the modification
  rule if I want to change my password? In this case, sentence A is semantically
  similar  to  B,  since  they  both  express  the desire for changing password.
  However, it's still reasonable to classify them into 2 intent classes, since A
  is asking for the method for changing password, while B is asking for the rule
  to follow when creating a new password.

@@

  The  above  limitation  motivates  us  to  propose a joint system of both text
  classification  task  and  sentence-pair  semantic  similarity task, named SFC
  here, shown in Fig. \ref{fig:ver.1.3}. Our goal is to utilize the advantage of
  the  feasibility  of  transfer learning based on semantic similarity, while in
  the  mean time, add the classification task's target into the training process
  of            sentence-pair           model           for           multi-task
  learning \cite{caruana1993multitask,collobert2008unified}.  To  obtain  such  a
  joint  system,  we  first start with preparation work, which is pre-training a
  sentence-pair   model   on  external  corpus  for  sentence  pair  duplication
  identification,  and  then  find  an auxiliary model or tool which can help us
  sample out top-K most related intent classes. This auxiliary model or tool can
  either  be searching engine such as elasticsearch \cite{divya2013elasticsearch}
  or  a  text  classification  model  trained  on  task-specific  chatbot  data.
  Afterwards,  we  further  fine-tune  the  sentence-pair  model with 2 training
  tasks:  1)  the  regular  sentence pair similarity tasks. Here we use the text
  classification  model  as  an auxiliary model in this paper to sample sentence
  pairs       for       training       based      on      negative      sampling
  strategy \cite{bamler2020extreme}.  The  reason is that a task-specific chatbot
  often  has hundreds of intent classes, which forms too many sentence pairs for
  training  since  any  two  sentences  from  two  different  classes can form a
  sentence-pair     of     negative     sample.     Besides,     according    to
  Bamler \cite{bamler2020extreme},   training   on  negative  samples  from  most
  confusing  wrong  label  can  help  model  converge  faster  and obtain better
  performance.  2) the classification task on top-K (here K is a hyperparameter)
  candidate  classes  provided  by  our auxiliary model or tool. Here we use the
  average  pooling  of  the  representation  given  by  sentence-pair  model for
  sentence pairs formed by the user input query and the corpus sentences in each
  class  as  the  feature.  We  stack the task-specific layers on the top of the
  shared-parameter  sentence-pair  model structure, which is a classic parameter
  sharing                                   mechanism \cite{collobert2008unified,
  subramanian2018learning,liu2019multi}   for  multi-task \cite{sun2019fine}.  In
  this  way, specific knowledge contained in these 2 tasks can be fully explored
  and deeply interact with each other to obtain better overall performance.

  However,  since  the auxiliary tool in joint system mentioned above works in a
  separate  stage  from  sentence-pair model, we find the the quality of sampled
  candidate  classes  might  limit  the  overall  performance  of SFC, since the
  candidate  classes  for  each user query is always fixed during the multi-task
  training  process. This observation motivates us to further improve SFC into a
  joint  model  of  sentence-pair  model  and  text  classification  model  in a
  hierarchical  architecture  by  putting  different  tasks at different network
  layers \cite{sogaard2016deep,   hashimoto2016joint}   and  then  training  them
  together,  shown  in  Fig  \ref{fig:framework}.  Here, the text classification
  model  involved in joint training process replace the role of auxiliary tools.
  In  this  way, the sentence pairs selected from top-K classes becomes dynamic,
  which  means  the  text classification model will also be further optimized to
  provide better top-K classes pooling result.

@@

  Before we start to fine-tune our sentence-pair model on task-specific dataset,
  we   first  fine-tune  RoBERTa  on  Quora  dataset \cite{iyer2017first},  which
  contains  404,290  potential  duplicate question pairs, for transfer learning.
  Then   we   continue  to  do  multi-task  training  on  sentence-pair  dataset
  $\mathcal{D'}$ sampled from the top-K candidate class labels provided by stage
  1.

@@

  \textbf{Amazon-670K}   is   a   customer   product  review  dataset  for  text
  classification  task from the extreme classification repository with full data
  containing  670,091  class  labels,  285,176  training samples and 150875 test
  samples \cite{bhatia2016extreme}.  As  the  data  set  contains  multiple class
  labels  per  training sample, we keep only the first class label for each data
  point. Besides, we also randomly sampled 250 class labels from all the classes
  that  contain only 5-15 data points. In this way, we simulate the low-resource
  chatbot  corpus setting with the subset of 1,942 training samples and 716 test
  samples for 250 class labels.

@@

  \textbf{HWU64}   is  a  intent  detection  dataset  designed  for  home  robot
  scenario \cite{liu2019benchmarking}.  It aims at the specific task of capturing
  the  intent  for  different  user  requests  to  home  robot  and  finding the
  corresponding answer. The raw dataset contains 25,716 data points for 64 class
  labels  through  crowdsourcing,  which  raises  much  more  data  than  common
  real-world  circumstances. Therefore, we experiment with the setups where only
  5,  10,  15  and 20 training data points are available for each class label by
  random sampling.

  \textbf{CLINC150}  is a dataset designed for task-oriented systems with 23,700
  queries  that  are  short  and unstructured for 150 intents, in the same style
  made  by real users through crowdsourcing \cite{larson2019evaluation}. Here, we
  sample 5, 10 and 15 training data points for each intent class label by random
  sampling for our experimental setup.

  \textbf{BANKING77}  is  a intent detection dataset for bank customer services.
  The    raw    dataset    contains    13,084   data   points   for   77   class
  labels \cite{casanueva2020efficient}.  Here,  we  sample 5, 10, 15, 20 training
  data  points  for  each  class  label  by random sampling for our experimental
  setup.

@@

  \textbf{Group  1:  single-task  classification  model.} This group of baseline
  models  are  based  on the network structure for classification model shown in
  \ref{Fig.1.sub.1}.   As   for   non-pretrained   neural   network,  we  choose
  TextCNN \cite{kim2014convolutional}  as  a  representative baseline. As for the
  pretrained  model,  we choose RoBERTa, BERT and ALBERT, all of which are among
  the  most  powerful pretrained models that achieve outstanding results in many
  NLP  tasks,  in  our  experimental  setting. Since we apply RoBERTa in our SFC
  system,   we   naturally  adopt  single-task  classification  model  based  on
  RoBERTa-large  and RoBERTa-base as our baseline models. Besides, we also adopt
  the       recently       released       baseline       pre-trained       model
  ALBERT-xxlarge \cite{lan2019albert}  for  comparison.  Since  we  use different
  few-shot   settings   from    \cite{casanueva2020efficient}  for  those  intent
  detection  datasets,  we also use BERT-large tuned on our few-shot settings as
  an essential reference for experimental results.
